Work Fragmentation in Developer Interaction Data

### 2016-08-01 paper_2.tex
Review 2.10, 2.14
minor changes

\begin{figure}
	\centering	
	\begin{minipage}[c]{0.30\linewidth}
		\small
		\centering
			\begin{tabular}{| p{2cm} |p{2cm} |} 
				\hline 
				stat & value \\  
				\hline 
				\hline 
				total & 4,284 \\
				min. & 2 min \\
				1st Qu. & 18 min\\
				median & 35 min \\
				mean & 48.91 min \\
				3rd Qu. & 62 min \\
				max. & 535 min\\
				\hline

@@

\begin{figure}
	\centering	
	\begin{minipage}[c]{0.30\linewidth}
		\small
		\centering
		\begin{tabular}{| p{2cm} |p{2cm} |} 
			\hline 
			stat & value \\  
			\hline 
			\hline 
			total & 15,825 \\
			min. & 2 min \\
			1st Qu. & 11 min\\
			median & 23 min \\
			mean & 35.87 min \\
			3rd Qu. & 47 min \\
			max. & 1,345 min\\
			\hline

@@

After this, we not only found evidence of the effect documented in related work, but also gained and reassured the confidence on the metrics we used as indicators of productivity and proceed to look with more detail this effect. So, in the third research question we investigated the productivity 30 minutes around the interruptions, finding a decrease below the median approximately 10 (UDC) to 20 (Mylyn) minutes before and after an interruption. The decrease after an interruption corresponds to the already documented recovery time or resumption time, which could last around to 15 minutes \cite{IH07, SBV98}.

We found interesting the similar decrease before the interruption occurs, about 15 minutes before it, that could be due to preparations before the interruption \cite{LVD06} (e.g. taking notes or leaving cues in the code) and/or the programmer's effort when trying to solve the problem that could have caused the interruption \cite{PD10}, which involves reading code, navigating around classes, debugging and more activities. We can see again this results in the fourth research question, and also a peak of productivity after the recovery time and several minutes before the next interruption.

In the third research question we identified three patterns of interruptions: positive, negative and neutral. We look closer to the activities performed during negative and positive interruptions in the fifth research question, where we set 11 categories of events and calculated the frequency of them after a each type of interruption. We found that assertive activities (e.g. editing, refactoring and saving changes) are more common after a positive interruption, and the comprehension activities (e.g. debugging and navigating around classes) are more common after a negative interruption. The second group of interruptions seems to be more disruptive as they require more time to reach the average productivity, and the activities are a reflection of the tasks performed during the recovery time ad mentioned by Parnin \cite{PR11}.

>>>>

\begin{figure}
	\centering	
	\begin{minipage}[c]{0.30\linewidth}
		\small
		\centering
			\begin{tabular}{| p{2cm} |p{2cm} |} 
				\hline 
				stat & value \\  
				\hline 
				\hline 
				total & 4,284 \\
				min. & 2 min \\
				1st Qu. & 18 min\\
				median & 35 min \\
				mean & 48.91 min \\
				3rd Qu. & 62 min \\
				max. & 535 min\\
				sd & 102.36 min\\
				\hline

@@

\begin{figure}
	\centering	
	\begin{minipage}[c]{0.30\linewidth}
		\small
		\centering
		\begin{tabular}{| p{2cm} |p{2cm} |} 
			\hline 
			stat & value \\  
			\hline 
			\hline 
			total & 15,825 \\
			min. & 2 min \\
			1st Qu. & 11 min\\
			median & 23 min \\
			mean & 35.87 min \\
			3rd Qu. & 47 min \\
			max. & 1,345 min\\
			sd & 43.95 min\\
			\hline

@@

After this, we not only found evidence of the effect documented in related work, but also gained and reassured the confidence on the metrics we used as indicators of productivity and proceed to look with more detail this effect. So, in the third research question we investigated the productivity 30 minutes around the interruptions, finding a decrease below the median approximately 10 (UDC) to 20 (Mylyn) minutes before and after an interruption. The decrease after an interruption corresponds to the already documented recovery time or resumption time, which could last 15 minutes \cite{IH07, SBV98} depending on the interruption.

We found interesting the similar decrease before the interruption occurs, about 15 minutes before it, that could be due to preparations before the interruption \cite{LVD06} (e.g. taking notes or leaving cues in the code) and/or the programmer's effort when trying to solve the problem that could have caused the interruption \cite{PD10}, which involves reading code, navigating around classes, debugging and more activities. However, Iqbal et al.  \cite{IH07} observed that after an alert the users took between 4 to 7 minutes to respond, and in the meantime they perform self-stabilizing actions before the interruption to have a more efficient recovery time. We can see again this results in the fourth research question, and also a peak of productivity after the recovery time and several minutes before the next interruption.

In the third research question we identified three patterns of interruptions: positive, negative and neutral. We look closer to the activities performed during negative and positive interruptions in the fifth research question, where we set 11 categories of events and calculated the frequency of them after a each type of interruption. We found that assertive activities (e.g. editing, refactoring and saving changes) are more common after a positive interruption, and the comprehension activities (e.g. debugging and navigating around classes) are more common after a negative interruption. We relate the first group of interruptions (in part) to the \textit{bug investigation} workflow described by LaToza et al. \cite{LVD06} and performed by programmers: after they found a problem and are unable to solve it, they consult teammates, documents, emails or artifacts to find a possible solution and then apply it. That would explain the assertive activities.

The second group of interruptions seems to be more disruptive as they require more time to reach the average productivity, and the activities are a reflection of the tasks performed during the recovery time as mentioned by Parnin \cite{PR11}, and they can be matched to the categories high-nav, debug and search, which are the common categories after a negative interruption.
